SI

### 2021-03-01 ms/manuscript.Rmd
Update MS: Add rel water means

```{r load-data}
tar_load(refs)
tar_load(refs_other)
tar_load(climate)
tar_load(filmy_species)
tar_load(moorea_sites)
tar_load(phylosig)
tar_load(range_comparison)
tar_load(combined_species_means)
tar_load(t_test_results)
tar_load(env_range_dt_model_summary)
tar_load(recovery_species_means)
tar_load(filmy_habit)
tar_load(filmy_phy)
tar_load(mean_vpd_sporo)
tar_load(mean_vpd_gameto)
tar_load(glmm_summary)
tar_load(glmm_params)
tar_load(env_range_dt_model)
tar_load(env_range_dt_model_summary)
tar_load(filmy_dt_chamber)
```

@@

# Extract p-values for species with gameto DT less than sporo
dt_g_less_than_s_pvals <-
t_test_results %>%
  filter(est_diff_sporo_gameto > 0, response == "recovery", p_value < 0.05) %>%
  pull(species) %>%
  map_chr(~ttest_pval(species_select = ., response_select = "recovery", data = t_test_results)) %>%
  knitr::combine_words()
```

@@

Control samples generally did not show any decrease in F~v~/F~m~ throughout the duration of the experiment (`r s_figure("dt-control")`). 
Relative water content reached \circa{ }0 % in the desiccated state (`r s_figure("water-all")`), and returned to \circa{ }100 % upon re-wetting in all species sampled (`r s_figure("water-s")`).

@@

Relative humidity in the growth chambers was high when samples were first inserted, then gradually decreased to the target value maintained by each drying salt (\figs{ }`r s_figure_num("chamber")`).
Brief fluctuations to higher humidities were observed when chambers were opened to insert or remove samples (`r s_figure("chamber-s")`).

>>>>

```{r load-data}
tar_load(refs)
tar_load(refs_other)
tar_load(climate)
tar_load(filmy_species)
tar_load(moorea_sites)
tar_load(phylosig)
tar_load(range_comparison)
tar_load(combined_species_means)
tar_load(t_test_results)
tar_load(env_range_dt_model_summary)
tar_load(recovery_species_means)
tar_load(filmy_habit)
tar_load(filmy_phy)
tar_load(mean_vpd_sporo)
tar_load(mean_vpd_gameto)
tar_load(glmm_summary)
tar_load(glmm_params)
tar_load(env_range_dt_model)
tar_load(env_range_dt_model_summary)
tar_load(filmy_dt_chamber)
tar_load(rel_water_species_means)
```

@@

# Extract p-values for species with gameto DT less than sporo
dt_g_less_than_s_pvals <-
t_test_results %>%
  filter(est_diff_sporo_gameto > 0, response == "recovery", p_value < 0.05) %>%
  pull(species) %>%
  map_chr(~ttest_pval(species_select = ., response_select = "recovery", data = t_test_results)) %>%
  knitr::combine_words()

# Rel. water content
rel_water_table <- 
rel_water_species_means %>%
  filter(!is.na(rel_water)) %>%
  group_by(salt, dry_time, rec_time) %>% 
  summarize(mean = mean(rel_water), sd = sd(rel_water), n = n(), .groups = "drop") %>%
  arrange(mean) %>%
  mutate(across(c(mean, sd), ~scales::percent(., suffix = " %", accuracy = 0.1))) %>%
  mutate(sum_val = glue("{mean} ± {sd} (*n* = {n})"))

rel_water_table %>% filter(salt == "LiCl", dry_time == "15") %>% pull(sum_val)
```

@@

Control samples generally did not show any decrease in F~v~/F~m~ throughout the duration of the experiment (`r s_figure("dt-control")`) and maintained RWC near 100% (\figs{ }`r s_figure_num("water-all")`, `r s_figure_num("water-s")`).

Relative water content in the desiccated state ranged from `r rel_water_table %>% filter(salt == "LiCl", dry_time == "15", rec_time == "desiccated") %>% pull(sum_val)` (--282 MPa for 15 d) to `r rel_water_table %>% filter(salt == "NaCl", dry_time == "2", rec_time == "desiccated") %>% pull(sum_val)` (--38 MPa for 2 d), and returned to \circa{ }100 % upon re-wetting in all species sampled (`r s_figure("water-s")`).

@@

Relative humidity in the growth chambers was high when samples were first inserted, then gradually decreased to the target value maintained by each drying salt (`r s_figure("chamber")`).
Brief fluctuations to higher humidities were observed when chambers were opened to insert or remove samples (`r s_figure("chamber-s")`).

### 2021-03-01 ms/si.Rmd
Update MS: Add rel water means

```{r sporophyte-dt-MgNO3, fig.height = 6.5, fig.width = 9, fig.cap = ""}
# Get mean times of each cluster of DT test samples for the selected drying salt
mgno3_clusters_2013 <- cluster_sporo_times(filter(sporo_times, str_detect(dataset, "2013")), "MgNO3", 3)
mgno3_clusters_2014 <- cluster_sporo_times(filter(sporo_times, str_detect(dataset, "2014")), "MgNO3", 1)

@@

```{r sporophyte-dt-NaCl, fig.height = 6.5, fig.width = 9, fig.cap = ""}
# Subset desiccation duration data
nacl_clusters_2012 <- filter(sporo_dt_times, salt == "NaCl") %>%
  mutate(
    serial_no = case_when(
      species %in% c(
        "Hymenophyllum_polyanthos", "Crepidomanes_humile", 
        "Crepidomanes_bipunctatum", "Polyphlebium_endlicherianum", 
        "Crepidomanes_minutum2") ~ "3200919",
      species == "Callistopteris_apiifolia" ~ "10140667, 10140659",
      TRUE ~ NA_character_
    )
  ) %>%
  mutate(year = "2012", species_duration = paste(species, dry_time))

>>>>

```{r sporophyte-dt-MgNO3, fig.height = 6.6, fig.width = 9, fig.cap = ""}
# Get mean times of each cluster of DT test samples for the selected drying salt
mgno3_clusters_2013 <- cluster_sporo_times(filter(sporo_times, str_detect(dataset, "2013")), "MgNO3", 3)
mgno3_clusters_2014 <- cluster_sporo_times(filter(sporo_times, str_detect(dataset, "2014")), "MgNO3", 1)

@@

```{r sporophyte-dt-NaCl, fig.height = 6.6, fig.width = 9, fig.cap = ""}
# Subset desiccation duration data
nacl_clusters_2012 <- filter(sporo_dt_times, salt == "NaCl") %>%
  mutate(
    serial_no = case_when(
      species %in% c(
        "Hymenophyllum_polyanthos", "Crepidomanes_humile", 
        "Crepidomanes_bipunctatum", "Polyphlebium_endlicherianum", 
        "Crepidomanes_minutum2") ~ "3200919",
      species == "Callistopteris_apiifolia" ~ "10140667, 10140659",
      TRUE ~ NA_character_
    )
  ) %>%
  mutate(year = "2012", species_duration = paste(species, dry_time))
